Week 5 - Chapter 7 pt.1 - Analysis

### 2024-10-02 week5.Rmd
correcitonweek5

---
title: "Week 5 - Chapter 7 pt.1 - Analysis"
author: "Verooo"
date: "2024-10-02"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

@@

## data were scraped at author level bceasier if you want to look at author "characteristics"

@@

## packages

@@

    (there is plenty of maths on this but in our case manually: our
    network density was too low, we looked at degree and reciprocity. We
    can increase the value of degree and try to approximate a value
    where changes in degree don't really make a change anymore. \
    Then we would change reciprocity parameter, in our case: increase
    it. We will have more reciprocity but also automatically increasing
    ties because reciprocity DEPENDS on ties\
    Thus, we need to find a way to do this automatically that can adjust
    both numbers at the same time.\
    We do not go about this ourselves though bc [as one may see] this is
    not very efficient)\
    \

@@

#### in paper report:

@@

and recalculate in probability ratio: take exponent of parameter value \
"if netw. increases in this stats by one the probability ration is
this."

>>>>

---
title: "Week 5 - Chapter 7 pt.1 - Analysis"
author: "Verooo"
date: "2024-10-02"
output: html_document
---

@@

***data were scraped at author level bc easier if you want to look at
author "characteristics"***

---

@@

## Packages

@@

    (there is plenty of maths on this but in our case manually: our
    network density was too low, we looked at degree and reciprocity. We
    can increase the value of degree and try to approximate a value
    where changes in degree don't really make a change anymore.\
    Then we would change reciprocity parameter, in our case: increase
    it. We will have more reciprocity but also automatically increasing
    ties because reciprocity DEPENDS on ties\
    Thus, we need to find a way to do this automatically that can adjust
    both numbers at the same time.\
    We do not go about this ourselves though bc [as one may see] this is
    not very efficient)\
    \

@@

# in paper report:

@@

and recalculate in probability ratio: take exponent of parameter value\
"if netw. increases in this stats by one the probability ration is
this."
